---
title: "e142 project"
author: "Justin Chow"
date: "5/17/2021"
output: html_document
---

Tasks
1. Find s.d. of salary - s.d. of team salaries
3. Measure of inequality - avgAST and sdPER (team value)
4. Control for total salary - salary cap for each team
5. Control for conference - west and east
6. Construct for years - 2016 to 2020 season
7. Find effect of salary on winning 


Evaluating NBA Team Performances with respect to Team's Salaries 

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir="C:/Users/14087/Documents/SCU_Spring2021/Econ 142/Project/nba")
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)

```

```{r setting, echo=FALSE, message=FALSE}
#Add a function to calculate corrected standard errors:
cse=function(reg) {
  rob=sqrt(diag(vcovHC(reg, type="HC1")))
  return(rob)
}

### Load the packages (all must have been installed)
library(doBy)
library(dplyr)
library(foreign)
library(knitr)
library(highcharter)
library(lmtest)
library(readstata13)
library(sandwich)
library(stargazer)
library(AER)
library(gdata)
library(tidyverse)
library(tibble)
library(ggplot2)
library(ggpubr)
library(readxl)
library(remotes)

```


```{r team stat, echo=TRUE, warning=FALSE, message=FALSE}
# use read_xl to load datasets 
nba_2016<-read_excel("nba_2016.xlsx")
nba_2017<-read_excel("nba_2017.xlsx")
nba_2018<-read_excel("nba_2018.xlsx")
nba_2019<-read_excel("nba_2019.xlsx")
nba_2020<-read_excel("nba_2020.xlsx")
nba<-rbind(nba_2016, nba_2017, nba_2018, nba_2019, nba_2020)

```


Descriptive Statistics Table

```{r data, echo=FALSE, warning=FALSE, message=FALSE}
nba$sdSalaries<-nba$sdSalaries/1000000
#Use stargazer to create a table of descriptive statistics
stargazer(as.data.frame(nba[c("win_percentage", "sdSalaries", "sdPER", "AST")]), 
          type="text", median=TRUE, digit=3, title="Descriptive Statistics")

```


Graphics

```{r plot, echo=FALSE, warning=FALSE, message=FALSE}
#Using ggplot, find whether there is a relationship between win_percentage and value of 2020 contracts.
ggplot(nba, aes(x=conference, y=win_percentage)) + 
  labs(title = "Win Percentage against NBA Conferences", x = "NBA Conference", y = "Win Percentage")+
  geom_boxplot(outlier.colour="red", outlier.shape=8, outlier.size=4)

```


```{r plot2, echo=FALSE, warning=FALSE, message=FALSE}
#Using ggplot, find whether there is a relationship between winning percentage and s.d. of team salaries.
ggplot(nba, aes(x=sdSalaries, y=win_percentage)) + geom_point(col="blue") + 
  labs(x = "s.d. of Team salaries", y = "Win percentage") +
  stat_smooth(method = "lm", col = "red") + 
  stat_regline_equation(label.x=12, label.y=.8) + 
  stat_cor(aes(label=..rr.label..), label.x=12, label.y=.75)

```


Regression Table

```{r reg, cho=TRUE, warning=FALSE, message=FALSE}
# log for s.d. of team salaries and team payroll
nba$sdSalaries<-nba$sdSalaries/1000000
nba$LNsdSalaries<-log(nba$sdSalaries)
# regress winning percentage and log for s.d. of team salaries along with control variables.
reg1<-lm(win_percentage~LNsdSalaries+conference, data=nba)
reg2<-lm(win_percentage~LNsdSalaries+conference+sdPER+AST, data=nba)
stargazer(reg1, reg2, type="text", se=list(cse(reg1), cse(reg2)), df=FALSE, digits=3)

```

